manuscript - APP

### 2018-09-25 R/manuscript_app.Rmd
new Figure 3b

if(!dir.exists(plot_pth)) {
  dir.create(plot_pth)
}
```

@@

```{r exp1b  - load data}
#df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
  filter(block != 0)

@@

## Figure 3

```{r Figure 3}
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
  ungroup()
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

@@

p <- accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
  theme(aspect.ratio = 1) + 
  scale_shape_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  scale_linetype_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  xlab("contrast") + ylab("Accuracy")
ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)
```

>>>>

if(!dir.exists(plot_pth)) {
  dir.create(plot_pth)
}

@@

```{r exp1b  - load data}
#df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
#  filter(block != 0)

@@

## Figure 3a

```{r Figure 3a}
df_exp1b %>% 
  ggplot(aes(x = targetk, y = accuracy) + 
    facet_grid(~restk, 
               labeller = labeller(
        xfacet = c(`2` = expression("Target's"~kappa~"=2"), 
                   `4` = expression("Target's"~kappa~"=4"),
                   `8` = expression("Target's"~kappa~"=8"),
                   `16` = expression("Target's"~kappa~"=16"),
                   `64` = expression("Target's"~kappa~"=64"))

    )) +
    stat_summary(fun.data = "mean_cl_boot") + 
    stat_summary(fun.y = mean, geom = "line") + 
    geom_hline(yintercept=0.125) + 
    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
    ylab("Accuracy") + 
    ylim(0,1)+
    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,32,64,128),labels = c("1","2","4","8","16","32","64","128"), trans = "log2") + 
    geom_vline(xintercept = restk_var, linetype = 2) +
    ggtitle(ggtit) +
    theme(plot.title = element_text(hjust = 0.5))
```

## Figure 3b

```{r Figure 3b}
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
  ungroup()
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

@@

p <- accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
  theme(aspect.ratio = 1) + 
  scale_shape_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  scale_linetype_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
  xlab("contrast") + ylab("Accuracy")
p
ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)
```
